SunPy - Python for Solar Physics

### 2014-08-28 3-3-HELIO.tex
fixes based on comments

\begin{listing}[h]
\pythoncode{pycode_helio.txt}
\caption{Example of querying the HEC service to multiple CME
catalogues, in this case the ones detected automatically 
by the Computer Aided CME Tracking feature recognition algorithm CACTus (\url{http://sidc.oma.be/cactus/}) \citep{robbrecht_automated_2009}.}
\label{code:helio}
\end{listing}

>>>>

\begin{listing}[h]
\pythoncode{pycode_helio.txt}
\caption{Example of querying the HEC service to multiple CME
catalogues, in this case the ones detected automatically 
by the by the Computer Aided CME Tracking feature recognition algorithm
\citep[CACTus - \url{http://sidc.oma.be/cactus/};][]{robbrecht_automated_2009}.}
\label{code:helio}
\end{listing}

### 2014-08-28 3-4-Helioviewer.tex
fixes based on comments

Reading JPEG2000 file into a SunPy session requires installing two
other pieces of software. The first, 
\url{http://www.openjpeg.org}{\texttt{OpenJPEG}}, is an open-source
library for reading and writing JPEG2000 files.  The other package 
required is 
\url{https://github.com/quintusdias/glymur}{\texttt{glymur}}, an
interface between Python and the OpenJPEG libraries (note that these
packages are {\it not} required to use the functionality described in
Section \ref{sssec:hv:png}).

>>>>

Reading JPEG2000 file into a SunPy session requires installing two
other pieces of software. The first, OpenJPEG
(\url{http://www.openjpeg.org}), is an open-source
library for reading and writing JPEG2000 files.  The other package 
required is Glymur (
\url{https://github.com/quintusdias/glymur}), an
interface between Python and the OpenJPEG libraries (note that these
packages are {\it not} required to use the functionality described in
Section \ref{sssec:hv:png}).
